A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-21 FMCAD2021/1_intro.tex
intro

\paragraph*{Structure}
After an introduction to background knowledge in Section~\ref{sec:pre}, we describe how to flatten a string constraint with string-integer conversion to an $\paexp$ formula in Section~\ref{sec:string-solving}. A decision procedure of $\paexp$ formulae is presented in Section~\ref{sec-dec}. We present optimizations in Section~\ref{sec-opt} and show the empirical evaluation results in Section~\ref{sec-exp}.

>>>>

\paragraph*{Structure}
After the preliminaries in Section~\ref{sec:pre}, we describe how to flatten a string constraint with string-integer conversion to an $\paexp$ formula in Section~\ref{sec:string-solving}. We present the quantifier elimination procedure for $\paexp$ in Section~\ref{sec-dec} and its optimizations in Section~\ref{sec-opt}. Finally, we describe the implementation and experiment results in Section~\ref{sec-exp}.
